Gelation as condensation frustrated by hydrodynamics and mechanical tension

### 2016-10-01 gel_cond/trunk/manuscript4.tex
Affiliation iLM depletion usual for colloids used in quantitative confocal

\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
%\thanks{These authors contributed equally to this work}
\author{Mathieu Leocmach}
\affiliation{Institut Lumière Matière, CNRS UMR 5306, Université Claude Bernard Lyon 1, Université de Lyon, Lyon, 69622 Villeurbanne Cedex, France}
%\thanks{These authors contributed equally to this work}
\author{Hajime Tanaka}
%\email{tanaka@iis.u-tokyo.ac.jp}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }

@@

Gelation of micron-size colloids is usually induced by depletion attractions due to polymers in the solvent. 

@@

We enclose the suspension in a thin microscopy cell sketched in Fig.~\ref{fig:cell_vs_cap}a. The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture. We introduce solid salt at the other end of the channel. Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, well revealing the depletion potential due to the pre-existing polymers. The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=10$ s. This method causes uniform gelation starting from the homogeneous Wigner crystal state without any solvent flow, allowing \textit{in situ} confocal microscopy observation throughout the process from $t \sim 0$.

>>>>

\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
%\thanks{These authors contributed equally to this work}
\author{Mathieu Leocmach}
\affiliation{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière, F-69622, VILLEURBANNE, France}
%\thanks{These authors contributed equally to this work}
\author{Hajime Tanaka}
%\email{tanaka@iis.u-tokyo.ac.jp}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }

@@

Gelation of micron-size colloids suitable for quantitative confocal microscopy is usually induced by depletion attractions due to polymers in the solvent. 

@@

We enclose the suspension in a thin microscopy cell sketched in Fig.~\ref{fig:cell_vs_cap}a. The bottom wall of the cell is an osmotic membrane providing contact with a long channel full of the same solvent mixture. We introduce solid salt at the other end of the channel. Salt dissolution and subsequent migration of the ions along the channel and through the membrane induce screening of the electrostatic repulsion, revealing the depletion potential well due to the pre-existing polymers. The time needed for the ions to diffuse from the membrane across the cell thickness is of the same order of magnitude as the Brownian time of the particles $\tau_B=10$ s. This method causes uniform gelation starting from the homogeneous Wigner crystal state without any solvent flow, allowing \textit{in situ} confocal microscopy observation throughout the process from $t \sim 0$.
